% Personal Information - Single Source of Truth
% This file contains all personal details used across CV templates

% Contact Information
\newcommand{\myname}{Julian Elliott}
\newcommand{\myfirstname}{Julian}
\newcommand{\mysurname}{Elliott}
\newcommand{\mytitle}{Senior Data Analyst \& Automation Specialist}
\newcommand{\myemail}{JulianPaulElliott@icloud.com}
\newcommand{\myphone}{+44 7925 859835}
\newcommand{\mylocation}{Tividale, Oldbury, West Midlands, UK}
\newcommand{\mylinkedin}{julianelliott}
\newcommand{\mygithub}{Julian-Elliott}
\newcommand{\myphoto}{julian-elliott-photo}

% Professional Summary
\newcommand{\mysummary}{Results-driven Senior Data Analyst and Automation Specialist with 14+ years of experience transforming complex data into actionable insights and automated processes. Expertise includes data analytics, process automation, Python, SQL, Tableau, Power BI, Blue Prism, UiPath, and mentoring teams. Proven track record of delivering £2M+ in annual savings through innovative automation solutions.}

% Personal Introduction (for CV header section)
\newcommand{\myintroduction}{%
Hello! I'm passionate about transforming raw data into actionable insights that drive real business value. With over 14 years of experience, I've evolved from inventory management to leading automation initiatives that delivered £2M+ in annual savings.

Currently expanding my expertise through an MSc in Data Analytics while building machine learning models and data pipelines. I thrive on solving complex problems through innovative technology solutions and mentoring teams to achieve their potential.

My approach combines technical expertise with business acumen, ensuring every project delivers measurable impact and sustainable value.
}

% Key Achievements (for easy reuse)
\newcommand{\savingsachievement}{£2M+ in annual savings}
\newcommand{\efficiencyachievement}{50\% efficiency improvements}
\newcommand{\salesachievement}{33\% sales growth}
\newcommand{\experienceyears}{14+ years}
